---
title: "Visuals"
output: github_document
date: "Last updated: February 13, 2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages

```{r}
library(tidyverse)
library(ggsignif)
```

## Loading in the Dataset

The dataset used for this project can be found in this project's repository under the `data` folder as `sr-dataset.cv`. It can be imported into your environment using the following code chunk:

```{r}
 sr.dataset <- read.csv("~/github/university-meat-reduction/data/sr-dataset.csv")
```

## Comparing Success Rates Across the Three Identified Approaches

```{r}
ggplot(sr.dataset,aes(x=approach,y=effect.dir,fill=effect.dir))
```


## Comparing Effect Estimates Across the Three Identified Approaches

```{r}

```


## Forest Plot

The fixed effect model used for our meta-analysis was restricted to the 17 interventions that utilized observational methods to evaluate changes in meat consumption.

```{r}
ggplot(sr.dataset,aes(x=effect.mag,y=study.title,color=approach)) + 
  geom_errorbar(aes(xmin=lower.ci,xmax=higher.ci),color="black",width=.2,size=.3) +
  geom_point(size=3) + 
  xlab("Estimated Effect Size") + 
  ylab(" ") + 
  scale_x_continuous(breaks=c(0,2,4,6,8),limits=c(0,8)) +
  labs(color="Approach") +
  scale_color_brewer(palette="Set2") +
  scale_y_discrete(limits=c("Garnett et al. (2020a)","Garnett et al. (2021)","Brunner et al. (2018)","Schwitzgebel, Cokelet, & Singer (2020)","Malan (2020)","Larner et al. (2021)","Kurz (2018)","Garnett et al. (2019)","Jalil, Tasoff, & Bustamante (2020)","Turnwald & Crum (2019)","Cerezo-Prieto & Frutos-Esteban (2021)","Piester et al. (2020a)","Piester et al. (2020b)","Slapø & Karevold (2019)","Andersson & Nelander (2021)","Michels et al. (2008)","Garnett et al. (2020b)")) + 
  theme(panel.grid.minor=element_blank())
```


