---
title: "Visuals"
output: github_document
date: "Last updated: February 13, 2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages

```{r}
library(ggplot2)
library(tibble)
library(ggsignif)
library(DiagrammeR)
```

## Loading in the dataset

The dataset used for this project can be found in this project's repository under the `data` folder as `sr-dataset.cv`. It can be imported into your environment using the following code chunk:

```{r}
sr.dataset <- read.csv("~/github/university-meat-reduction/data/sr-dataset.csv")

print(as_tibble(sr.dataset))
```

## Reporting on search results

grViz(diagram="digraph flowchart {
      node [fontname=arial,shape=rectangle]
      tab1[label='@@1']
      tab2[label='@@2']
      tab3[label='@@3']
      tab4[label='@@4']
      tab5[label='@@5']
      tab6[label='@@6']
      tab7[label='@@7']
      tab8[label='@@8']
      tab9[label='@@9']
      tab1 -> tab3 -> tab5 -> tab6 -> tab8 -> tab9;
    }
      [1]:'Records identified from databases (n=13,607):|ERIC (n=106)|PsycINFO (n=206)|PubAg (n=6,900)|PubMed (n=1,522)| Scopus (n=1,567)|SocAb (n=489)|Web of Science (n=756)'
      [2]:'Duplicates removed (n=2,061)'
      [3]:'Records screened (n=11,546)'
      [4]:'Records excluded (n=11,460)'
      [5]:'Articles retrieved (n=86)'
      [6]:'Articles assesses for eligibility (n=86)'
      [7]:'Articles excluded (n=56)'
      [8]:'Selected articles (n=29)'
      [9]:'Selected studies (n=31)'
    ")

## Exploring the implementation and publication rates of included studies

First, we'll have to load in the transformed dataset documenting the cumulative frequency with which the included studies were conducted and published by year.

```{r}
times.series <- read.csv("~/github/university-meat-reduction/data/time-series.csv")
```


```{r}
ggplot(times.series,aes(x=year,y=cumul.freq,fill=fill)) +
  geom_col(position="dodge") +
  scale_fill_brewer(palette="RdPu",guide=guide_legend(title=NULL)) +
  scale_x_continuous(breaks=c(2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021)) +
  xlab(" ") +
  ylab("Cumulative Frequency") +
  scale_y_continuous(breaks=c(1,11,21,31)) +
  theme(panel.background=element_blank(),legend.position="bottom",panel.border=element_rect(fill=NA))
```

## Comparing success rates across the three ddentified approaches

```{r}
ggplot(sr.dataset,aes(x=approach,y=num.study,fill=effect.dir)) + 
  geom_col(position="fill",alpha=.8) + 
  scale_fill_manual(values =c("paleturquoise3","goldenrod1"),guide=guide_legend(title=NULL)) +
  scale_x_discrete(labels=c("Choice Architecture (n=5)","Conscious Processing (n=16)","Multimodal (n=10)")) +
  scale_y_continuous(labels=scales::percent_format(.1L),breaks=c(1,.6,.437,0)) +
  xlab(" ") + 
  ylab("Rate of Success") +
  theme(legend.position="bottom",panel.border=element_rect(fill=NA),panel.background=element_blank())
  
```

## Creating a dataframe for the fixed effect model

```{r,eval=FALSE}
fixed.effect <- filter(sr.dataset,outcome.var=="Observed Changes")
```

```{r,eval=FALSE}
write.csv(fixed.effect,"~/github/university-meat-reduction/data/fixed-effect.csv")
```


```{r}
fixed.effect <- read.csv("~/github/university-meat-reduction/data/fixed-effect.csv")

print(as_tibble(fixed.effect))
```

## Comparing the estimated effect sizes across individual studies

```{r}
ggplot(fixed.effect,aes(x=effect.mag,y=study.title,fill=approach)) + 
  geom_errorbar(aes(xmin=lower.ci,xmax=higher.ci),color="black",width=.2,size=.3) +
  geom_point(alpha=.5,size=6,shape=21) + 
  xlab("Estimated Effect Size") + 
  ylab(" ") + 
  scale_x_continuous(breaks=c(0,2,4,6,8),limits=c(0,8)) +
  labs(color=" ") +
  scale_fill_brewer(breaks=c("Multimodal","Choice Architecture","Conscious Processing"),palette="Set2",labels=c("Multimodal (n=10)","Choice Architecture (n=5)","Conscious Processing (n=16)")) +
  scale_y_discrete(limits=c("Garnett et al. (2020a)","Garnett et al. (2021)","Brunner et al. (2018)","Schwitzgebel, Cokelet, & Singer (2020)","Malan (2020)","Larner et al. (2021)","Kurz (2018)","Garnett et al. (2019)","Jalil, Tasoff, & Bustamante (2020)","Turnwald & Crum (2019)","Cerezo-Prieto & Frutos-Esteban (2021)","Piester et al. (2020a)","Piester et al. (2020b)","Slapø & Karevold (2019)","Andersson & Nelander (2021)","Michels et al. (2008)","Garnett et al. (2020b)")) + 
  theme(legend.position="bottom",panel.background=element_blank(),panel.border=element_rect(fill=NA),panel.grid.minor=element_blank())
```

## Comparing effect estimates across the three identified approaches

```{r}
ggplot(fixed.effect,aes(x=effect.mag,y=approach,fill=approach)) +
  geom_violin(adjust=1.2,alpha=0.8,size=.3) + 
  stat_summary(fun="mean",geom="point",shape=21,fill="black",size=3) +
  scale_y_discrete(limits=c("Conscious Processing","Choice Architecture","Multimodal")) +
  scale_fill_brewer(palette="Set2",breaks=c("Multimodal","Choice Architecture","Conscious Processing"),labels=c("Multimodal (n=10)","Choice Architecture (n=5)","Conscious Processing (n=16)")) +
  xlab("Mean Effect Size") + 
  ylab(" ") +
  labs(fill=" ") +
  coord_cartesian(xlim=c(.9,3.6)) +
  theme(legend.position="bottom",panel.border=element_rect(fill=NA),panel.background=element_blank(),axis.ticks.y=element_blank(),axis.text.y=element_blank(),panel.grid.minor=element_blank())
```
