---
title: "Visuals"
output: github_document
date: "Last updated: February 13, 2023"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages

```{r}
library(ggplot2)
library(ggsignif)
library(DiagrammeR)
```

## Loading in the Dataset

The dataset used for this project can be found in this project's repository under the `data` folder as `sr-dataset.cv`. It can be imported into your environment using the following code chunk:

```{r}
sr.dataset <- read.csv("~/github/university-meat-reduction/data/sr-dataset.csv")

print(sr.dataset)
```

## Reporting on Search Results

grViz(diagram="digraph flowchart {
      node [fontname=arial,shape=rectangle]
      tab1[label='@@1']
      tab2[label='@@2']
      tab3[label='@@3']
      tab4[label='@@4']
      tab5[label='@@5']
      tab6[label='@@6']
      tab7[label='@@7']
      tab8[label='@@8']
      tab9[label='@@9']
      tab1 -> tab3 -> tab5 -> tab6 -> tab8 -> tab9;
    }
      [1]:'Records identified from databases (n=13,607):|ERIC (n=106)|PsycINFO (n=206)|PubAg (n=6,900)|PubMed (n=1,522)| Scopus (n=1,567)|SocAb (n=489)|Web of Science (n=756)'
      [2]:'Duplicates removed (n=2,061)'
      [3]:'Records screened (n=11,546)'
      [4]:'Records excluded (n=11,460)'
      [5]:'Articles retrieved (n=86)'
      [6]:'Articles assesses for eligibility (n=86)'
      [7]:'Articles excluded (n=56)'
      [8]:'Selected articles (n=29)'
      [9]:'Selected studies (n=31)'
    ")


## Comparing Success Rates Across the Three Identified Approaches

```{r}
ggplot(sr.dataset,aes(x=approach,y=effect.dir,fill=effect.dir))
```
## Creating a Dataframe for our Fixed Effect Model

```{r,eval=FALSE}
fixed.effect <- filter(sr.dataset,outcome.var=="Observed Changes")
```

```{r}
write.csv(fixed.effect,"~/github/university-meat-reduction/data/fixed-effect.csv")
```


```{r}
fixed.effect <- read.csv("~/github/university-meat-reduction/data/fixed-effect.csv")

print(fixed.effect)
```

## Comparing Effect Estimates Across the Three Identified Approaches

```{r}
ggplot(sr.dataset,aes(x=effect.mag,y=approach,fill=approach)) +
  geom_violin(alpha=0.8) + 
  scale_fill_brewer(palette="Set2")
```

## Forest Plot

The fixed effect model used for our meta-analysis was restricted to the 17 interventions that utilized observational methods to evaluate changes in meat consumption.

```{r}
ggplot(sr.dataset,aes(x=effect.mag,y=study.title,color=approach)) + 
  geom_errorbar(aes(xmin=lower.ci,xmax=higher.ci),color="black",width=.2,size=.3) +
  geom_point(alpha=.8,size=3) + 
  xlab("Estimated Effect Size") + 
  ylab(" ") + 
  scale_x_continuous(breaks=c(0,2,4,6,8),limits=c(0,8)) +
  labs(color="Approach") +
  scale_color_brewer(palette="Set2") +
  scale_y_discrete(limits=c("Garnett et al. (2020a)","Garnett et al. (2021)","Brunner et al. (2018)","Schwitzgebel, Cokelet, & Singer (2020)","Malan (2020)","Larner et al. (2021)","Kurz (2018)","Garnett et al. (2019)","Jalil, Tasoff, & Bustamante (2020)","Turnwald & Crum (2019)","Cerezo-Prieto & Frutos-Esteban (2021)","Piester et al. (2020a)","Piester et al. (2020b)","Slapø & Karevold (2019)","Andersson & Nelander (2021)","Michels et al. (2008)","Garnett et al. (2020b)")) + 
  theme(panel.grid.minor=element_blank())
```


